EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-06 draft.tex
listing labels

Developers can add new algorithm as stateless functions in
several ways and with two levels of integration. In the first level of
integration, the algorithm execution is not dependent on an initial
configuration created in the setup, and it only needs to take messages from the
input queue and return the modified population to the output queue. On the
second level, the algorithm receives a configuration from the initial setup,
specifying initial algorithm parameters. We show an example of the configuration
file received by workers in Figure x. % Adding to Annex or is not even needed? - M

% Clarify this is the first level.
In the case of a decoupled worker, developers can implement a new stateless
Docker container that executes a daemon that continuously pulls messages from the
input queue on the Redis host specified as an environmental variable {\tt REDIS\_HOST}.
If the function is written in Python, developers can base the implementation on
the provided worker container image, adding a new type of function.  % say which function, what's its API, how can you test it - JJ
If developers use an existing library for population-based algorithms, they need
to change the standard model of execution, that first creates a random
population because, in this case, we need to start with the population provided
as a parameter. Depending on the implementation, % Depending on which implementation? - JJ
it is required to extract the
population from the JSON message and create the population object needed by the
library. Again, the state of the population must be encoded as a JSON message to
be returned as a result. Depending on the type of experiment, additional data
can be returned in the message. % how do you know the type of experiment? how do you add that? Which JSON key? - JJ
For instance, the message can include the id of
the container, or even records giving information for each iteration of the
algorithm. % Is this mandatory? Optional? How is the algorithm going to use it? - JJ
The format of the JSON message is depicted in Figure y. % Adding to Annex or is not even needed? - M
% it's probably OK if you add it, but instead of Figure it could be a listing - JJ

@@

% This is the second level? - JJ
Algorithm developers can upload the container definition or images directly to
DockerHub; another option is to upload the container image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub; this
can be defined in DockerHub (or any other registry) too.u 
% This is probably accessory. What difference would it make to upload it to GitHub?
% You also need to say in this section how it helps your overall objective. Does it contribute to reproducibility? We've talked about that elsewhere. Does it help diversity by making easy to add new algorithms? - JJ

@@

After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script
that takes as argument the experiment id to generate a collection of files containing all the
data generated by the experiment in a JSON format.

>>>>

Developers can add new algorithm as stateless functions in
several ways and with two levels of integration. In the first level of
integration, the algorithm execution is not dependent on an initial
configuration created in the setup, and it only needs to take messages from the
input queue and return the modified population to the output queue. On the
second level, the algorithm receives a configuration from the initial setup,
specifying initial algorithm parameters. We show an example of the configuration
file received by workers in  Listing \ref{code:config}. % Adding to Annex or is not even needed? - M

\begin{lstlisting}[language=Python, caption = Configuration message example, label=code:config]
{"problem":{
  "name":"BBOB","instance": 1,"error":1e-8,"function":4,
  "dim":3,"search_space":[-5,5],
  "problem_id":"1515-4-1-3",
  "max_iterations": 20,"population":[],
  "population_size": 100,
  "algorithm": "GA",  
  "params":{
      "GA":{"crossover": { "type": "cxTwoPoint", 
            "CXPB_RND": [0.2, 0.6], "CXPB": 0.26},
             "mutation": { "MUTPB_RND": [0.1, 0.3], 
             "indpb": 0.05, "sigma": 0.5, 
             "type":"mutGaussian","mu":0,"MUTPB":0.12},
             "selection": { 
               "type": "tools.selTournament", 
               "tournsize": 2 },
               "iterations": 50},
       "PSO": {"Vmax":5,"wMax":0.9,"wMin":0.2,
               "c1":2,"c2":2,"iterations":50 } 
    },
  "experiment":{"type":"benchmark","experiment_id": 1515}
  }
}
\end{lstlisting}

% Clarify this is the first level.
In the case of a decoupled worker, developers can implement a new stateless
Docker container that executes a daemon that continuously pulls messages from the
input queue on the Redis host specified as an environmental variable {\tt REDIS\_HOST}.
If the function is written in Python, developers can base the implementation on
the provided worker container image, adding a new type of function.  % say which function, what's its API, how can you test it - JJ
If developers use an existing library for population-based algorithms, they need
to change the standard model of execution, that first creates a random
population because, in this case, we need to start with the population provided
as a parameter. Depending on the implementation, % Depending on which implementation? - JJ
it is required to extract the
population from the JSON message and create the population object needed by the
library. Again, the state of the population must be encoded as a JSON message to
be returned as a result. Depending on the type of experiment, additional data
can be returned in the message. % how do you know the type of experiment? how do you add that? Which JSON key? - JJ
For instance, the message can include the id of
the container, or even records giving information for each iteration of the
algorithm. % Is this mandatory? Optional? How is the algorithm going to use it? - JJ
The format of the JSON message is depicted in  Listing \ref{code:result}. % Adding to Annex or is not even needed? - M
% it's probably OK if you add it, but instead of Figure it could be a listing - JJ

\begin{lstlisting}[language=Python, caption=Fragment of output message, label=code:result ]
{
"time_stamp": 1588455316.698875,
"evals": [
  {
    "gen_num": 0, "best_fitness": -259.96925945939404,
    "best_solution": [ -4.9446848321611405, 
                        2.593007989886873, 
                        2.0011025031167673],
    "num_of_evals": 17
  },
  {
    "gen_num": 49, "best_fitness": -419.47555780783347,
    "best_solution": [ -0.9165294450108963, 
                        2.291966676472422, 
                        1.8527006568795485],
    "num_of_evals": 28
  }
],
"worker_id": "4f5eb12e-8278-40de-b0f3-4ac18171566d",
"message_counter": 1,
"message_id": "cbcd2e82-e232-4818-8aec-2cd072c7cfe9",
"best_score": -419.47555780783347
}
\end{lstlisting}

@@

% This is the second level? - JJ
Algorithm developers can upload the container definition or images directly to
DockerHub; another option is to upload the container image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub; this
can be defined in DockerHub (or any other registry) too.u

% This is probably accessory. What difference would it make to upload it to GitHub?
% You also need to say in this section how it helps your overall objective. Does it contribute to reproducibility? We've talked about that elsewhere. Does it help diversity by making easy to add new algorithms? - JJ

@@

After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script
that takes as argument the experiment id to generate a collection of files containing all the
data generated by the experiment in a JSON format as shown in Listing \ref{code:exp}.

\begin{lstlisting}[language=Python, caption=Experiment configuration example, label=code:exp]
{
"DIM_CONFIGURATION" : 
 {
 "2":{"GEN":40,"POP_SIZE": 50,"MAX_ITER":10,"MESSAGES":10},
 "3":{"GEN":25,"POP_SIZE": 60,"MAX_ITER":20,"MESSAGES":10},
 "5":{"GEN":28,"POP_SIZE": 60,"MAX_ITER":30,"MESSAGES":10},
 "10":{"GEN":50,"POP_SIZE": 70,"MAX_ITER":30,"MESSAGES":10},
 "20":{"GEN":66,"POP_SIZE":100,"MAX_ITER":30,"MESSAGES":10},
 "40":{"GEN":80,"POP_SIZE":125,"MAX_ITER":40,"MESSAGES":10}
 },
"GA_WORKER_RATIO" : 0.5,
"FUNCTIONS": [4],
"DIMENSIONS" : [2, 3, 5, 10, 20, 40],
"CXPB_RND": [0.2, 0.6],
"MUTPB_RND": [0.1, 0.3]
}
\end{lstlisting}
